Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-07-31 Ben_Manuscripts/Paper1/methods.tex
revisions

An ensemble of characteristic, low-energy vacuum monomer configurations
were constructed by applying a simulated annealing process to a
parameterized monomer. Monomers were cooled from 1000K to 50K over 10
nanoseconds. A low energy configuration was pulled from the trajectory 
and charges were reassigned using the am1bccsym method of molcharge
shipped with Openeye Scientific software's QUACPAC. Using the new
charges, the monomer system was annealed again and multiple monomer
configurations were pulled from the trajectory to be used for full
system construction.

@@

Each pore consists of twenty stacked monomer layers with periodic 
continuity in all directions, avoiding any edge effects and creating an
infinite length pore ideal for studying transport. A small number of
layers is preferred in order to reduce computational cost and to allow
us look at longer timescales. Ultimately, we chose to build a system
with 20 layers of monomer in each pore in order to give sufficient
resolution when simulating X-ray diffraction patterns.

>>>>

An ensemble of characteristic, low-energy vacuum monomer configurations
were constructed by applying a simulated annealing process to a
parameterized monomer. Monomers were cooled from 1000K to 50K over 10
nanoseconds. A low energy configuration was pulled from the trajectory 
and charges were reassigned using the am1bccsym method of molcharge
shipped with Openeye Scientific software's QUACPAC. Using the new
charges, the monomer system was annealed again and monomer
configurations were pulled from the trajectory to be used for full
system construction.

@@

A typical simulation volume contains four pores in a monoclinic unit cell,
the smallest unit cell that maintains hexagonal symmetry when extended 
periodically. Each pore is made of twenty stacked monomer layers with
% describe unit cell in terms of alpha beta gamma angles?
% mention semi-isotropic pressure coupling here or later
periodic continuity in all directions, avoiding any edge effects and 
creating an infinite length pore ideal for studying transport. A small
number of layers is preferred in order to reduce computational cost and 
to allow us to look at longer timescales. Ultimately, we chose to build a system
with 20 layers of monomer in each pore in order to give sufficient
resolution when simulating X-ray diffraction patterns.
